Augraphy: A Data Augmentation Library for Document Images

### 2023-04-29 paper.tex
revert to previous format, update augmentations table

\begin{table}[]
    \centering
    \caption{Individual \emph{Augraphy} augmentations for each augmentation phase, in suggested position within a pipeline. Augmentations that work well in more than one phase are listed in the last column.}
    \resizebox{0.9\textwidth}{!}{
    \begin{tabular}{llll}
    \toprule
        \textbf{Ink Phase} & \textbf{Paper Phase} & \textbf{Post Phase} & \textbf{Multiple} \\
        \midrule
        \textsf{BleedThrough} & \textsf{ColorPaper}& \textsf{BadPhotoCopy} & \textsf{BrightnessTexturize} \\
        \textsf{LowInkLines} & \textsf{Watermark} & \textsf{BindingsAndFasteners} & \textsf{DirtyDrum} \\
        \textsf{InkBleed} & \textsf{Gamma} & \textsf{BookBinding} & \textsf{DirtyRollers} \\
        \textsf{Letterpress} & \textsf{LightingGradient} & \textsf{Folding} & \textsf{Dithering} \\
        & \textsf{SubtleNoise} & \textsf{JPEG} & \textsf{Geometric}\\
        & \textsf{DelaunayTessellation} & \textsf{Markup} & \textsf{NoiseTexturize}\\
        & \textsf{VoronoiTesselation} & \textsf{Faxify} & \textsf{Scribbles}\\
        & \textsf{PatternGenerator}& \textsf{PageBorder} & \\
        & & & \\
        \bottomrule
    \end{tabular}}
    \label{tab:augmentations}
\end{table}

>>>>

\begin{table}[]
    \centering
    \caption{Individual \emph{Augraphy} augmentations for each augmentation phase, in suggested position within a pipeline. Augmentations that work well in more than one phase are listed in the last column.}
    \resizebox{0.9\textwidth}{!}{
    \begin{tabular}{llll}
    \toprule
        \textbf{Ink Phase} & \textbf{Paper Phase} & \textbf{Post Phase} & \textbf{Multiple} \\
        \midrule
        \textsf{BleedThrough} & \textsf{ColorPaper}& \textsf{BadPhotoCopy} & \textsf{BrightnessTexturize} \\
        \textsf{LowInkPeriodicLines} & \textsf{Watermark} & \textsf{BindingsAndFasteners} & \textsf{DirtyDrum} \\
        \textsf{LowInkRandomLines} & \textsf{Gamma} & \textsf{BookBinding} & \textsf{DirtyRollers} \\
        \textsf{InkBleed} & \textsf{LightingGradient} & \textsf{Folding} & \textsf{Dithering} \\
        \textsf{Letterpress} & \textsf{SubtleNoise} & \textsf{JPEG} & \textsf{Geometric}\\
        & \textsf{DelaunayTessellation} & \textsf{Markup} & \textsf{NoiseTexturize}\\
        & \textsf{VoronoiTesselation} & \textsf{Faxify} & \textsf{Scribbles}\\
        & \textsf{PatternGenerator}& \textsf{PageBorder} & \textsf{LinesDegradation}\\
        & & & \textsf{Brightness}\\
        \bottomrule
    \end{tabular}}
    \label{tab:augmentations}
\end{table}
